Evidence accumulation for tackling research waste (Supplement)

### 2020-01-27 Manuscript/SuppMat.Rmd
update 27.01.2020

    }
       [1]: 'Questions are relevant to stakeholders'
      [2]: 'Appropriate design & methods used'
      [3]: 'Unbiased reporting'
      [4]: 'Accessible full publication'
      [5]: 'Wasteful research'
      [6]: 'Evidence synthesis'
      [7]: 'Utilisable research' 
      [8]: 'Previous knowledge not accounted for'
      [9]: 'Poor design; \\nquestionable research practices'
        ", height=1000)

>>>>

    }
       [1]: 'Research question'
      [2]: 'Study design & methods'
      [3]: 'Reporting'
      [4]: 'Accessible full publication'
      [5]: 'Wasteful research'
      [6]: 'Evidence synthesis'
      [7]: 'Utilisable research' 
      [8]: 'Previous knowledge not accounted for'
      [9]: 'Poor design; \\nquestionable research practices'
                ", height=1000)
